---
title: "W_UP_01"
author: "Alondra Garcia"
date: "Summer 2022"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->
position are categorical variable. Push-ups is a numerical variable. I will do an analysis that explains push-ups based on position
# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results
```{r}
boxplot(pushups~position,data=mydata)
```


there is pushups on the y axis of the box plot. The average push ups for the positions appears to be different. The skills positions appears to have more pushups based off the y axis.

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(pushups~position,data=mydata)
```
## Inferential Results


The median for both positions has a very big difference. It appears the median for the skill position is higher then the line positions. The max the line position can do is 34 push ups while the skill can do up to 108. From the data results it seems that skill positions is far more capable to do the most push ups.

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(pushups~position,data=mydata)
```


Our p-value is 0.000009421. Our df is 27.079. And our t vaule is -5.4341. Our alternative hypothesis is shown. It states true difference in means between group line and group skill is not equal to 0. Mean in group line is 17.12500, mean group in skill is 49.72727. If our null hypothesis is true, the p vaule is the probability of getting our results. Line vs skills. it is rare the p value is low we would reject the null hypothesis.

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The original question was "Who could do the most pushups? The skill position or the line positions under a specific amount of time?" Our response based off of our numerical description results & our inferential results can see that the skill position can do more push ups than the Line position under any amount of time given. We used a box plot & a table to figure out our values and percentages. The median and average were much higher for the skill positions 


